### 2021-03-26 Appendix-A/Appendix-A.tex
Updates from Overleaf

\begin{lstlisting}[language=bash]
$ git clone https://github.com/s3team/Abacus.git
$ cd Abacus
$ ./docker.sh
\end{lstlisting}

@@

\subsection{Quantify the leakage}
To analyze the execution trace and generate the report, run the below command:
\begin{lstlisting}[language=bash]

$ ./build/App/QIF/QIF ./Inst_data.txt -f Function.txt \ 
  -d ./examples/a.out -o result.txt
\end{lstlisting}

>>>>

\begin{lstlisting}[language=bash, frame=none, numbers=none]
$ git clone https://github.com/s3team/Abacus.git
$ cd Abacus
$ ./docker.sh
\end{lstlisting}

@@

\subsection{Quantify the leakage}
To analyze the execution trace and generate the report, run the below command:
\begin{lstlisting}[language=bash]
$ ./build/App/QIF/QIF ./Inst_data.txt -f Function.txt \ 
  -d ./examples/a.out -o result.txt
\end{lstlisting}
